\section{Publications}
$\dagger$ Graduate student working under my supervision. \quad $\star$ Co-first authors.
\begin{etaremune}
\item $\text{\me{A.C. Murph}}^\star$, L.J. $\text{Beesley}^\star$, G.C. Gibson, L.A. Castro, S.Y. Del Valle, \& D.A. Osthus (2026). Beyond Equal Weights: A Disease-agnostic Approach to Ensemble Learning for Infectious Disease Forecasting. \textbf{Accepted to Nature Communications.}
\item \me{A.C. Murph}, J.P. Williams, \& J. Hannig (2025). Generalized fiducial inference on differentiable manifolds. \textbf{International Journal of Approximate Reasoning}, p.109618, ISSN 0888-613X 
\item \me{A.C. Murph}, M.F. Dorn, S. Bhat, A. Nachtsheim, K.J. Kuhn, A.C. Olson, S.M. Andrade, \& L. Tandon (2025). Unique \& challenging aspects of plutonium metal standards exchange program for actinide measurements. \textbf{Journal of Radioanalytical and Nuclear Chemistry}. 
\item \me{A.C. Murph}, G.C. Gibson, L.B. VanDervort, N. Panda, L.A. Castro, S.Y. Del Valle, C.A. Manore, \& D.A. Osthus (2025). Mapping incidence and prevalence peak data for SIR forecasting applications. \textbf{Journal of Mathematical Biology}, 91(70). 
\item $\text{\me{A.C. Murph}}^\star$, G.C. $\text{Gibson}^\star$, E.B. $\text{Amona}^\dagger$, L.B. VanDervort, L.A. Castro, S. Y. Del Valle, \& D.A. Osthus (2025). Synthetic method of analogues for emerging infectious disease forecasting. \textbf{PLOS Computational Biology}, 21(6): e1013203. 
\item Y. Liu, J. Hannig, \& \me{A.C. Murph} (2025). A Geometric Perspective on Bayesian and Generalized Fiducial Inference, \textbf{Statistical Sciences} 40(2), 219-234. 
\item J.D. Strait, K.R. Moran, \me{A.C. Murph}, J.D. Hyman, H.S. Viswanathan \& P. Stauffer (2025). Covariate-informed multi-fidelity bias correction of distributions, \textbf{Accepted to SIAM/ASA Journal on Uncertainty Quantification.}
\item J.D. Hyman, \me{A.C. Murph}, L. Boampong, A. Navarre-Sitchler, G. Srinivasan, J.W. Carey, \& H.S. Viswanathan (2024). Determining the dominant factors for carbon mineralization in three-dimensional fracture networks, \textbf{International Journal of Greenhouse Gas Control}, 139, 104-265.
\item \me{A.C. Murph}, J.D. Strait, K.R. Moran, J.D. Hyman, H.S. Viswanathan, \& P.H. Stauffer (2024).  Sensitivity analysis in the presence of intrinsic stochasticity for discrete fracture network simulations, \textbf{Journal of Geophysical Research: Machine Learning and Computation}, 1, e2023JH000113.
\item \me{A.C. Murph}, J.D. Strait, K.R. Moran, J.D. Hyman, \& P.H. Stauffer (2024). Visualisation and outlier detection for probability density function ensembles, \textbf{Stat}, 13(2), e662.
\item \me{A.C. Murph}, J. Hannig, \& J.P. Williams (2023). Introduction to generalized fiducial inference.  In J. Berger, X. Meng, N. Reid, \& M. Xie (Eds.) \textbf{Handbook of Bayesian, Fiducial, and Frequentist Inference} (Ch. 13).  Chapman \& Hall. 
\item E. Faden, A. Mitchell, \me{A.C. Murph}, T. Myers, \& N. Ryan (2021). Mr. Hulot’s invisible gorilla: Jacques Tati and inattentional blindness, \textbf{Projections}, 15(2), 1-29.
\item \me{A.C. Murph}, A. Flynt, \& B.R. King (2021).  Comparing finite sequences of discrete events with non-uniform time intervals, \textbf{Sequential Analysis}, 40(3), 291-313.
\end{etaremune}
\textit{Manuscripts in review/preparation:}
\begin{itemize}
\item \me{A.C. Murph}, C.B. Storlie, P.M. Wilson, J.P. Williams, \& J. Hannig (202x). Bayes Watch: Bayesian change-point detection for process monitoring with fault detection, \textsc{In Review}. 
\item E.C. Lawrence, \me{A.C. Murph}, S.A. Vander Wiel, \& C. Liu (202x). A New Method for Multinomial Inference using Dempster-Shafer Theory. \textsc{In Review.}
\end{itemize}